### 2019-03-12 papers/journal/encoding.tex
fixed wide space problem

\subsubsection{Fixing VTS by learning activity functions:}

Now we consider a scenario where some of the activity functions for
some of the molecules are missing.
%
The activity functions are $\mu$-input Boolean functions.
%
First, we choose a class of formulas for the candidate functions.
%
We encode the candidates in a formula with parameters.
%
By assigning different values for the parameters, a solver may select
different candidates for the activity functions.
%
We will illustrate only one class of formulas.
%
However, we support other classes of formulas, for example, $k$-CNF.

In the following, the formula \texttt{NNFTemplate} encodes a set of
negation normal form functions that take $y_1,..,y_\mu$ as input and
contain $\lambda$ literals.
%
We use $\texttt{Gate}$ to encode a gate that takes a parameter integer
$x$ to encode various gates.
%
We use $\texttt{Leaf} $ to encode the literal at some position.
%
Both are stitched to define \texttt{NNFTemplate}.
%
To encode the set of NNF formulas with $\lambda$ literals, it has
finite-range integer variables
$z_1,..,z_{2\lambda}$ as parameters.

% \paragraph{Encoding low depth cnf circuits}
% \paragraph{Encoding boolean gates}

\begin{align*}
&\texttt{Gate}( x, w_1, w_2 ) = ( x  = 1 \limplies w_1  \land w_2 ) \land  
( x = 2  \limplies w_1  \lor w_2 ) \\
&\texttt{Leaf}( x, [y_1,..,y_\mu] ) =
\Land\limits_{l=1}^{\mu} ( x = 2l-1  \limplies y_{l}) \land ( x = 2l  \limplies \lnot y_{l})\\
&\texttt{NNFTemplate}([z_1,..,z_{2\lambda}],[y_1,..,y_\mu] ) = \\
&\exists w_1,..,w_{2\lambda}.\;w_1 \land \Land_{l=1}^{\lambda} w_{\lambda+l} = \texttt{Leaf}( z_{\lambda+l}, [y_1,..,y_\mu] ) \land
w_{l} = \texttt{Gate}( z_l, w_{2l},w_{2l+1})
\end{align*}

Using the template we define the constraints $\texttt{FindFunctions}(z,\lambda)$
that encodes the candidate functions that satisfy the activity requirements,
where $z$ is the vectors of parameters for encoding parameters
for each molecule,
and $\lambda$ limits the size of the candidate functions. 
%
We fix the all other aspects of the VTS to be fixed via constraints
$\texttt{FixedForFunctions}$.
%
\begin{align*}
&\texttt{FindFunctions}(z,\lambda) =\\
&\Land \{ \bigwedge\limits_{i} n_{i,m} \limplies a_{i,m} = 
\texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) \\
& \hspace{8cm}|
\nodef_m \text{ is undefined}\} \\
&\Land \{ \bigwedge\limits_{i,j,q} e_{i,j,q,m} \limplies b_{i,j,q,m} = 
\texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) \\
& \hspace{8cm} | \edgef_m \text{ is undefined}
\}\\
& \texttt{FixedForFunctions} = \texttt{PresentCons} \land\\
& \quad \quad
\lnot \Lor \texttt{AbsentE} \;\union\; \texttt{AbsentELabel} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthFunction}(z,\lambda) = \\
& \quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForFunctions} \land \texttt{FindFunctions}(slimit) )
\end{align*}
We construct $\texttt{SynthFunction}(z,\lambda)$ similar to the earlier
variations.
%
By reading of the values of $z$ in a satisfying model of the formula,
we learn the synthesized function.

>>>>

\subsubsection{Fixing VTS by learning activity functions:}
Now we consider a scenario where some of the activity functions for
some of the molecules are missing.
%
The activity functions are $\mu$-input Boolean functions.
%
First, we choose a class of formulas for the candidate functions.
%
We encode the candidates in a formula with parameters.
%
By assigning different values for the parameters, a solver may select
different candidates for the activity functions.
%
We will illustrate only one class of formulas.
%
However, we support other classes of formulas, for example, $k$-CNF.

In the following, the formula \texttt{NNFTemplate} encodes a set of
negation normal form functions that take $y_1,..,y_\mu$ as input and
contain $\lambda$ literals.
%
We use $\texttt{Gate}$ to encode a gate that takes a parameter integer
$x$ to encode various gates.
%
We use $\texttt{Leaf} $ to encode the literal at some position.
%
Both are stitched to define \texttt{NNFTemplate}.
%
To encode the set of NNF formulas with $\lambda$ literals, it has
finite-range integer variables
$z_1,..,z_{2\lambda}$ as parameters.
% \paragraph{Encoding low depth cnf circuits}
% \paragraph{Encoding boolean gates}
%
\begin{align*}
&\texttt{Gate}( x, w_1, w_2 ) = ( x  = 1 \limplies w_1  \land w_2 ) \land  
( x = 2  \limplies w_1  \lor w_2 ) \\
&\texttt{Leaf}( x, [y_1,..,y_\mu] ) =
\Land\limits_{l=1}^{\mu} ( x = 2l-1  \limplies y_{l}) \land ( x = 2l  \limplies \lnot y_{l})\\
&\texttt{NNFTemplate}([z_1,..,z_{2\lambda}],[y_1,..,y_\mu] ) = \\
&\exists w_1,..,w_{2\lambda}.\;w_1 \land \Land_{l=1}^{\lambda} w_{\lambda+l} = \texttt{Leaf}( z_{\lambda+l}, [y_1,..,y_\mu] ) \land
w_{l} = \texttt{Gate}( z_l, w_{2l},w_{2l+1})
\end{align*}
%
Using the template we define the constraints $\texttt{FindFunctions}(z,\lambda)$
that encodes the candidate functions that satisfy the activity requirements,
where $z$ is the vectors of parameters for encoding parameters
for each molecule,
and $\lambda$ limits the size of the candidate functions. 
%
We fix the all other aspects of the VTS to be fixed via constraints
$\texttt{FixedForFunctions}$.
%
\begin{align*}
&\texttt{FindFunctions}(z,\lambda) =\\
&\Land \{ \bigwedge\limits_{i} n_{i,m} \limplies a_{i,m} = 
\texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) \\
& \hspace{8cm}|
\nodef_m \text{ is undefined}\} \\
&\Land \{ \bigwedge\limits_{i,j,q} e_{i,j,q,m} \limplies b_{i,j,q,m} = 
\texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) \\
& \hspace{8cm} | \edgef_m \text{ is undefined}
\}\\
& \texttt{FixedForFunctions} = \texttt{PresentCons} \land\\
& \quad \quad
\lnot \Lor \texttt{AbsentE} \;\union\; \texttt{AbsentELabel} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthFunction}(z,\lambda) = \\
& \quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForFunctions} \land \texttt{FindFunctions}(slimit) )
\end{align*}
We construct $\texttt{SynthFunction}(z,\lambda)$ similar to the earlier
variations.
%
By reading of the values of $z$ in a satisfying model of the formula,
we learn the synthesized function.
